---
title: "CADS R Web Scraping Workshop"
output:
  html_document:
    df_print: paged
---

## Load necessary packages:
```{r}
library(tidyverse)
library(rvest)
library(devtools)
library(gridExtra)
```

## Read in data from website:
```{r}
URL="https://www.sports-reference.com/cbb/play-index/matchup_finder.cgi?request=1&year_min=1950&year_max=2022&school_id=duke&opp_id=north-carolina&game_type=A&game_month=&game_location=&game_result=&is_overtime=&comp_school=le&comp_opp=le&rank_school=ANY&rank_opp=ANY&order_by=date_game&order_by_asc=&offset=0"
UNC = URL %>%
  read_html() %>%
  html_table(fill=T) %>% #creates a list of all tables on webpage
  .[[1]] #selecting table we want

head(UNC)
```

## Clean the data:

- Change the column names since some column names are missing and to clarify the data frame
- Remove the empty columns, remove **School** and **Opp** variables since they are repetitive
```{r}
colnames(UNC) = c("Year","Date","Empty","School","Rank_Duke","Home_Team","Opp","Rank_UNC","Winner","Empty",
                  "Duke_Pts","UNC_Pts","MOV","Empty","OT")
UNC = select(UNC, -c(3,10,14,"School","Opp"))
```

- Make all columns with numbers numeric variables rather than characters so we can do calculations with them
- Automatically fills in NA values now
```{r}
UNC = mutate_at(UNC,c(3,5,7:10), as.numeric)
```

- Remove extra heading rows
```{r}
UNC = UNC[-c(21,42,63,84),]
```

- Fix **Winner** variable
```{r}
UNC$Winner = ifelse(UNC$Winner == "W","Duke","UNC")
```

- Fix **Home_Team** variable
```{r}
UNC$Home_Team = ifelse(UNC$Home_Team == "@","UNC","Duke")
```

- Fix **OT** by filling in 0 for any missing observations
```{r}
UNC$OT = ifelse(is.na(UNC$OT),0,UNC$OT)
```

- Take absolute value of MOV
```{r}
UNC$MOV = abs(UNC$MOV)
```


## Calculations:

Average points for each team and average point differntial
```{r}
UNC_avg = mean(UNC$UNC_Pts)
Duke_avg = mean(UNC$Duke_Pts)
MOV_avg = mean(UNC$MOV)

cat("The average number of points UNC has scored against Duke is", UNC_avg, sep='\n')
cat("The average number of points Duke has scored against UNC is",Duke_avg, sep='\n')
cat("The average point differential is",MOV_avg, sep='\n')
```


Maximums:
```{r}
UNC_max_points = max(UNC$UNC_Pts)
Duke_max_points = max(UNC$Duke_Pts)
MOV_max_value = max(UNC$MOV)

cat("The max number of points UNC has scored against Duke is", UNC_max_points, sep='\n')
cat("The max number of points Duke has scored against UNC is",Duke_max_points, sep='\n')
cat("The max point differential was",MOV_max_value, sep='\n')
```

## Visuals:

Point differentials over time:
```{r}
ggplot(UNC) +
  geom_point(aes(Year,MOV, color=Winner)) +
  theme(axis.text.x = element_text(angle = 90))
```


Distribution of each team's points
```{r}
p1 = ggplot(UNC) +
  geom_boxplot(aes(UNC_Pts), color="skyblue2") +
  xlab("UNC Points") +
  xlim(45,105)
p2 = ggplot(UNC) +
  geom_boxplot(aes(Duke_Pts), color='blue4') +
  xlab("Duke Points") +
  xlim(45,105)

LAYOUT=matrix(c(1,2,1,2),ncol=2)
grid.arrange(p1,p2,layout_matrix=LAYOUT)
```


## Probabilities

Chance of UNC winning if game goes to overtime
```{r}
overtime_games = filter(UNC,OT>0) #games that went into overtime
ot_games_won = filter(overtime_games,Winner=="UNC") #overtime games where UNC won

ot_win = nrow(ot_games_won)/nrow(overtime_games)
cat("UNC has won",ot_win*100,"percent of their games against Duke in overtime :(. But, note that the sample size is small.")
```

Chance of home team winning:
```{r}
home_team_wins = filter(UNC,Home_Team == Winner) #games where home team wins

home_wins_prob = nrow(home_team_wins)/nrow(UNC)
cat("The home team has won",home_wins_prob*100,"percent of games!")
```



